---
output: github_document
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Cycling Infrastructure Analysis (assignment1)

<!-- badges: start -->
<!-- badges: end -->

The goal of this package is to download, classify, and visualize cycling infrastructure data from OpenStreetMap. It builds spatial cycling networks, classifies infrastructure by safety type, computes summary statistics, and produces maps and plots for analysis.

## Installation

You can install the development version of assignment1 from [GitHub](https://github.com/) with:

``` r

devtools::install_github("al415615/assignment1")```

## Example

This is a basic example which shows you how to solve a common problem:

```{r pressure, echo = FALSE}
## Example

```{r example}
library(assignment1)

# Download cycling network
net <- get_cycling_network("Muenster, Germany")

# Print and plot network
net
plot(net)

# Classify infrastructure
classif <- classify_bike_infrastructure(net)

# Print and plot classification
classif
plot_cycling_safety_map(classif)
```

<!-- badges: start -->
<!-- badges: end -->

This package was developed as part of a university assignment on spatial data analysis and cycling infrastructure accessibility.